---
title: "Memo"
author: "Arunima Roy, Andrew Nalundasan, Jianan Hsu"
date: "11/20/2020"
output: html_document
---


```{r, include=FALSE}
# Sets the working directory
setwd("~/Documents/School/Grad School/5112 Stats for Business Analytics/data_translation_20201116")

# Sourcing the code
source('01_code/read_file_draft.R')

library(stargazer)
```

#### Background:

The goal for this case study was to investigate how agricultural profits are determined in Ghana. Our first task was to find out how household educational attainment and certain characteristics of the local area has on agricultural profit. We have acquired those results and wanted to take it a step further by studying which ecological zone also yields the best profits. While looking at both of these scenarios, we dove in to understand how profit per area unit is affected.   

To clearly state everything, we have two questions that we are trying to answer in this case study:

1)	What is the effect of a household’s educational attainment on agricultural profit? 

2)	Which ecological zone promotes the highest agricultural profit?

#### Results: 
The results to the questions stated in this case study and its interpretations are represented below: 

1) Having some level of education attainment within a household unfortunately decreases agricultural profit by 2.65 cedi. 

2) When observing the ecological zones on its own in the model, proves to be a statistically significant variable at the 0% statistical level. 

When running the model to view the each of these zones individually, we get that the coastal zone yields 6.393e+05 more profit than the other zones, coming out to be the least profit yielded. The forest zone decreases profits by 8.160e+05 more compared to the coastal zone. The savannah zone decreases profits by 9.785e+05 more compared to the coastal zone.

The graph below shows most profitable ecological zones. 

Figure 1:

```{r, echo = FALSE}
library(ggplot2)
wrangle_data_final %>% 
  group_by(ez) %>% 
  ggplot(aes( x = ez)) + 
    geom_col(aes(y = agri1c))

```


#### Recommendations:
My recommendations to you would be the following:


1) With regards to educational attainment and profits, I would advise to target sales efforts towards a community that has a primary education facility/school.


2) My second recommendation would be a more of a criteria when locating the right place to target agricultural profits. I would suggest finding an area that is as close to a forest-like ecological zone, along with finding a community that has a primary education school.


## Statistical Analysis 
This section will focus on the analysis of the models the team ran as well as our findings. During our study, we focused on how agricultural profit in Ghana is affected by variables collected during the GLSS 4 survey.  


#### Correlation Matrix
The variables with the highest correlation was between loc2 (urban&local) and the Permanent Market variable with a coefficient of .87. 

The second highest correlation was between clust and ecological zone with a coefficient of .86. 

```{r, echo = FALSE}
round_cor
```


#### Results for each model:

##### Regression 1:

```{r, echo = FALSE}
stargazer(regression_1, type = "text")
```

We referred to ‘regression_1’ as our ‘Base Model’. Our aim for this model was to cast the net wide to find variables with statistical significance based on our initial assumptions. Multiple steps were taken to check the validity of our base model using the Residual Standard Error, Multiple R-Squared, and our p-value. We ensured that our correlation matrix had no NA’s included. Through this base model, we found eight variables with statistical significance. These variables were:

Dependent variable:

agric1c (HH agro income(1)-corrected): We used ‘agric1c’ as our dependent variable since this is what represents profit to us. We measured against the other explanatory variables to see the effect, if any, they had on profit.

Explanatory variables with statistical significance:

land_own_by_HH (Land owned by HH): This was included because we needed to know if a particular household owning land or not would affect profits of agricultural land. Owning land must be true in order to grow crops and make profits. ‘land_own_by_HH’ was found to be statistically significant at the 1% level of significance with a p-value of 2.09e-4

tot_val_harvest (Total Value of Harvest): This was included so that we could see how the total value of harvests effected profit. Our assumption was that the higher the total value of harvest, the higher profits would be made. ‘tot_val_harvest’ was found to be statistically significant at the 1% level of significance with a p-value of 8.68e-4

totemp (Income from employment): We were interested to see how income from other employment would affect profits of agricultural land. We assumed that if one who profits from agricultural land must tend to the land, meaning this would be their main job. We were interested to see if other forms of employment would affect profits from agricultural land. ‘totemp’ was found to be statistically significant at the 5% level of significance with a p-value of 1.35e-3

hhagdepn (Depreciation of farm equipment): Quality gear is paramount for any profession. In order to be successful, you must be able to depend on the tools that you help you accomplish your objective. A higher rate of depreciation of farm equipment would indicate higher expenditures on farm equipment for replacements, maintenance, or upgrades. We included this variable to see if investing more money in higher quality farm equipment would affect profitability form the agricultural land. ‘hhagdepn’ was found to be statistically significant at the 1% level of significance with a p-value of 6.12e-15

expfoodc (Expenditure on food by households): There is a decent effect on profit from the amount of money spent on food for the household.  ‘expfoodc’ was found to be statistically significant at the 10% level of significance with a p-value of 0.012

impfoodc (Imputed food exp.-correlated): We had assumed that imputed food and agricultural profits would have a direct relationship. This would make sense since the families that are selling the food would also be able to grow some for themselves to eat. ‘impfoodc’ was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16.
road (Presence of a road in the town): ‘road’ was found to be statistically significant at the 1% level of significance with a p-value of 6.36e-05.

profit_per_unit (Land owned by HH): We mutated this variable to add to our dataset. This variable takes our dependent profit variable (‘agric1c’) and divides it by the ‘land_own_by_HH’ variable in order to calculate a rate of profit based on the ‘unit_plot_areas’. ‘profit_per_unit’ was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16.

Model validation:

Regression 1 Histogram:

```{r, echo = FALSE}
std_dist_1
```

Our histogram is normally distributed with a residual count above 2500. This histogram test is used to check for model validity. When a histogram shows normally distributed errors, this means that this model is a good model to use for regression testing. 


Regression 1 Fitted:

```{r, echo=FALSE}
plot(fitted(regression_1), resid(regression_1),
     xlab = "Fitted", ylab = "Residuals",
     abline(h = 0, col = "blue"))
```

We checked for constant variance using the Fitted vs. Residual plot. As we can see, there is a concentration of data points within a set range. This tells us that there is constant variance in this model with most of our data points concentrated in this general area with the exception of a few outliers. 


##### Regression 2:

```{r, echo = FALSE}
stargazer(regression_2, type = "text")
```


Our intent for ‘regression_2’ was to check how the highest education level of a household effects agricultural profit. Through this model, we found six variables with statistical significance. These variables were:

Dependent variable:

agric1c (HH agro income(1)-corrected): same as ‘regression_1’.

Explanatory variables with statistical significance:

ez (Ecological Zone of household): We were especially interested in the effect of characteristics of local areas had on profit. Ecological Zones were broken up into three distinct factors: Coastal, Forest, and Savannah. ‘ez’ was found to be statistically significant at the 1% level of significance with a p-value of 4.12e-06

unit_plot_areas (Unit of plot areas): We included this variable because we needed to factor in the size of the plots of land that we were working with so that we could see what the rate of profit was per unit of plot area. ‘unit_plot_areas’ was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16

road (road): We discovered that areas with roads that connect the community had a positive effect on profit of agricultural land. This makes sense since transportation of goods is essential to meet the demands of the community.  ‘road’ was found to be statistically significant at the 1% level of significance with a p-value of 3.94e-05

permanent_market (Permanent market): We wanted to see how significant the presence of a permanent market would have on profit of agricultural land. Our assumption was that this would be strongly significant. ‘permanent_market’ was found to be statistically significant at the 10% level of significance with a p-value of 0.0336

highest_educ (Highest level of education in household): We were especially interested in what effect household educational attainment had on profit of agricultural land. Our assumption was that higher education attainment would lead to higher profits but were surprised to see that the relationship shows a negative trend. Now our assumption is that highly educated individuals don’t go into farming for their main source of income. ‘highest_educ’ was found to be statistically significant at the 10% level of significance with a p-value of 0.0185

profit_per_unit:land_own_by_HH (profit_per_unit * land_own_by_HH): We created an interaction between ‘profit_per_unit’ and ‘land_own_by_HH’. This interaction tells us the effect of profit per unit varying by if land is owned by a household. This interaction was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16.

Model validation:

Regression 2 Histogram:

```{r, echo=FALSE}
std_dist_2
```

Our histogram  for regression 2 is also normally distributed. This histogram test is used to check for model validity. When a histogram shows normally distributed errors, this means that this model is a good model to use for regression testing. 

Regression 2 Fitted:

```{r, echo=FALSE}
plot(fitted(regression_2), resid(regression_2),
     xlab = "Fitted", ylab = "Residuals",
     abline(h = 0, col = "blue"))
```

Similar to the histogram from regression 1, our fitted graph appears shows a concentration of data points within a set range. This tells us that there is constant variance in this model with most of our data points concentrated in this general area with the exception of a few outliers.


##### Regression 3:

```{r, echo = FALSE}
stargazer(regression_3, type = "text")
```

Our intent for ‘regression_3’ was to perform Interaction testing between ecological zone and locality as well as profit per unit and land owned by household. We wanted to see what adding an additional interaction would do to our model. Through this model, we found nine variables with statistical significance. These variables were:

Dependent variable:

agric1c (HH agro income(1)-corrected): same as ‘regression_1’ and ‘regression_2’.

Explanatory variables with statistical significance:

ez (Ecological Zone of household): The significance of this variable held from ‘regression_2’ to ‘regression_3’.  ‘ez’ was found to be statistically significant at the 10% level of significance with a p-value of 0.016276

loc2 (Locality classification): We were especially interested in the effect of characteristics of local areas had on profit and ‘loc2’ differentiates ‘rural’ vs. ‘urban’ localities. ‘loc2’ was found to be statistically significant at the 5% level of significance with a p-value of 0.004

unit_plot_areas (Unit of plot areas): The significance of this variable held from ‘regression_2’ to ‘regression_3’. ‘unit_plot_areas’ was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16

road (road): The significance of this variable held from ‘regression_2’ to ‘regression_3’.  ‘road’ was found to be statistically significant at the 1% level of significance with a p-value of 1.16e-4

permanent_market (Permanent market): The significance of this variable held from ‘regression_2’ to ‘regression_3’.  ‘permanent_market’ was found to be statistically significant at the 10% level of significance with a p-value of 1.96e-2

primary_school (Completion of Primary School): This variable was included to see if the effect of education changed between the completion of Primary School compared to the highest level of education. Our summary tells us that individuals that reached primary school educational attainment had a positive relationship to profit, while ‘highest_educ’ was a negative relationship. ‘primary_school’ was found to be statistically significant at the 10% level of significance with a p-value of 0.034662

highest_educ (Highest level of education in household): The significance of this variable held from ‘regression_2’ to ‘regression_3’. ‘highest_educ’ was found to be statistically significant at the 10% level of significance with a p-value of 0.011

ez:loc2 (ez * loc2): We created this interaction between ‘ez’ and ‘loc2’. This interaction tells us the effect of ecological zone varying by locality classification. This interaction was found to be statistically significant at the 1% level of significance with a p-value of 9.41e-05.

profit_per_unit:land_own_by_HH (profit_per_unit * land_own_by_HH): The significance of this interaction held from ‘regression_2’ to ‘regression_3’. This interaction was found to be statistically significant at the 1% level of significance with a p-value of < 2e-16.

Model validation:

Regression 3 Histogram:

```{r, echo=FALSE}
std_dist_3
```

Our histogram  for regression 3 is also normally distributed. This histogram test is used to check for model validity. When a histogram shows normally distributed errors, this means that this model is a good model to use for regression testing.

Regression 3 Fitted:

```{r, echo=FALSE}
plot(fitted(regression_3), resid(regression_3),
     xlab = "Fitted", ylab = "Residuals",
     abline(h = 0, col = "blue"))
```

Similar to the histogram from regression 1 and 2, our fitted graph appears shows a concentration of data points within a set range. This tells us that there is constant variance in this model with most of our data points concentrated in this general area with the exception of a few outliers.
